Galois Characterization of Function Fields of \\ Transcendence Degree $1$ over Number Fields

### 2016-12-18 Master Thesis/synopsis.tex
Minor edits
Fix
Add proof of 5.2 (iii)

\begin{lemma}
Let $v\in\operatorname{Spv}(K)$. Then we have:
\[\operatorname{rank}(v)\leq \operatorname{rrank}(v)\quad\text{and}\quad\operatorname{rrank}(v)+\dim k(v)\leq\dim(K) \]
\end{lemma}

@@

\begin{proposition}\label{2.6}
Let $K_0/K$ be an algebraic extension.
\begin{enumerate}[(i)]
\item Suppose there exists a prime number $\ell$ with $\ell^\infty\nmid[K_0:K]$ and such that for every algebraic extension $L/K_0$ we have: 
\[ \mathrm{H}^3(L,\mathbb{Z}/\ell\mathbb{Z}) = \begin{cases}
\mathbb{Z}/\ell\mathbb{Z}, & \ell^\infty\nmid [L:K_0]\\
0, & \text{otherwise}
\end{cases} \]
Then there exists a unique henselian $w\in|\operatorname{Spv}(K)|$.
\item Assume that (i) is satisfied for two different prime numbers. Then $w$ is defectless.
\end{enumerate}
\end{proposition}

@@

Now $(K_0)_{w_1}$ is henselian both with respect to $w_1$ and with respect to the prolongation of $w_0$. Lemma \ref{2.2} yields $\operatorname{cd}(G_{(K_0)_{w_1}})\leq 2$, a contradiction. The uniqueness of $w$ is again a consequence of Lemma \ref{2.2}.
\item Choose the prime $\ell$ different from $\operatorname{char} k(w)$. According to Lemma \ref{2.5} we have $\operatorname{rrank}(w)=\dim_\mathbb{Q}(\Gamma_w\otimes_\mathbb{Z}\mathbb{Q} )\geq \dim_{\mathbb{F}_\ell}(\Gamma_w /\ell\Gamma_w) = 2 = \dim(K)$.
\end{enumerate}
\end{proof}

@@

Let $v\in\operatorname{Spv}_\text{d}^{(1)}$ and let $N$ be the normal subgroup of $G_{K_v}$ generated by all subgroups $G_{K_w}$ for $w\in\operatorname{Spv}_\text{rd}^{(2)}(K)$ with $v(w) = v$. Since a global field has no non-trivial algebraic extension in which every prime splits completely we get $N=G_{K_v}$. This shows $K'_{v'} := (K_v)'$ is a henselization of $K'$ with respect to $v'=\sigma(v)$. Furthermore, let $w_1,w_2\in\operatorname{Spv}_\text{rd}^{(2)}(K)$ with $w_1\neq w_2$ and $v=v(w_1)=v(w_2)$, then:
\[ \sigma(G_{K^\text{t}_v}) = \sigma(G_{K_{w_1}}\cap G_{K_{w_2}}) = G_{K'_{w'_1}}\cap G_{K'_{w'_2}} = G_{(K')^\text{t}_{v'}} \]
Therefore, $\sigma$ induces an isomorphism:
\[ G_{k(v)} \cong G_{K_v}/G_{K_v^\text{t}} \to G_{K'_{v'}}/G_{(K')_{v'}^\text{t}}\cong G_{k(v')} \]
The rest follows from the Theorem of Neukirch-Uchida.
\end{proof}

@@

\begin{proof}
\begin{enumerate}[(i)]
\item  We have $(K^\text{t}_P)^\times/n\cong \mathbb{Z}/n\mathbb{Z}$ since $\operatorname{char}k(P) = 0$. The canonical map $K^\times\to (K^\text{t}_P)^\times/n$ can be identified with the map $K^\times /n\to\mathbb{Z}/n$ induced by $v_P$. Now the following commutative diagram gives us the result:
\[ \begin{tikzcd}
0 \ar[d] & 0 \ar[d]\\
U_{P'}/n \ar[r, dashed]\ar[d] & U_P/n\ar[d]\\
K'^\times /n \ar[r, "\varphi_n"]\ar[d] & K^\times/n\ar[d]\\
(K^\text{t}_P)'^\times /n \ar[r, "\varphi_n"'] &  (K^\text{t}_P)^\times /n
\end{tikzcd}\]
\item Consider the field extension $K_P/K$. Without loss of generality, we can assume $K=K_P$. Then $r_P/n$ is an isomorphism and the composition
\[\begin{tikzcd}
k(P)^\times / n\ar[rr, "(r_P/n)^{-1}"] && U_P/n \ar[r, hook] & K_P^\times/n
\end{tikzcd}\]
is the inflation $\mathrm{H}^1(k(P), \mu_n) \to \mathrm{H}^1(K_P,\mu_n)$. The same holds for $P'$ due to Lemma \ref{3.2}. Therefore, the assertion follows from the commutativity of the following diagram:
\[ \begin{tikzcd}
k(P')^\times/n \ar[r, "\cong"] \ar[d, "\varphi_P/n"'] & \mathrm{H}^1(k(P'),\mu_n) \ar[r, "\mathrm{inf}"] \ar[d]& \mathrm{H}^1(K'_{P'}, \mu_n) \ar[d, "\varphi_n"] \\
k(P)^\times/n \ar[r, "\cong"'] & \mathrm{H}^1(k(P),\mu_n)  \ar[r, "\mathrm{inf}"'] & \mathrm{H}^1(K_{P}, \mu_n)
\end{tikzcd}  \qedhere\]
\end{enumerate}
\end{proof}

@@

\begin{lemma}\phantomsection\label{5.2}
\begin{enumerate}[(i)]
\item Let $f: A\to B$ be a homomorphism of abelian groups with finite kernel and cokernel. Then $A$ is free-by-finite iff $B$ is free-by-finite.
\item Let $0\longrightarrow A'\stackrel{i}{\longrightarrow}A\stackrel{p}{\longrightarrow}A''\longrightarrow 0$ be an exact sequence of abelian groups. If $A'$ and $A''$ are free-by-finite, then $A$ is free-by-finite. Conversely, if $A$ is free-by-finite, then $A'$ is free-by-finite. If additionally, $A'$ is finitely generated, then $A''$ is free-by-finite.
\item Let $A$ be free-by-finite. Then $\bigcap_{n\in\mathbb{N}}nA=0$.
\end{enumerate}
\end{lemma}

@@

Now let $B$ be free-by-finite and $K = \ker(f)$. Since the injective map $A/K \to B$ induced by $f$ can be restricted to their torsion subgroups, we see that $(A/K)_\text{tor}$ is finite. Every $a\in A_\text{tor}$ can be written as $a = a' + k$ for some $a'\in A,\ k\in K$ such that $na'\in K$ for some $n\in\mathbb{N}$. Since both $(A/K)_\text{tor}$ and $K$ are finite, $A_\text{tor}$ is finite as well. TODO
\item TODO
\item It suffices to show this assertion for finite groups and for $A=\mathbb{Z}$. For $A$ finite we have $nA = 0$ for $n = \#A$. Since $\mathbb{Z}$ has no nilpotent elements, the intersection of all prime ideals of $\mathbb{Z}$ is already trivial. \qedhere
\end{enumerate}
\end{proof}

@@

\begin{proof}
\begin{enumerate}[(i)]
\item Let $\mathcal{P}(F)$ be the group of principal ideals of $F$. Consider the following exact sequence:
\[ \begin{tikzcd}
1 \ar[r] & \mathcal{O}_F^\times \ar[r] & F^\times \ar[r]& \mathcal{P}(F) \ar[r] & 1
\end{tikzcd} \]
By Dirichlet's Unit Theorem, $\mathcal{O}_F^\times$ is free-by-finite. $\mathcal{P}(F)$, as a subset of the ideal group of $F$, is free abelian, in particular free-by-finite. The assertion follows from Lemma \ref{5.2} (ii).
\item Consider the following exact sequence:
\[ \begin{tikzcd}
1 \ar[r] & \displaystyle \prod_{i=1}^{n-1} F_i^\times \ar[r]& \displaystyle \Big(\prod_{i=1}^{n}F_i^\times\Big)/F^\times \ar[r]& F_n^\times/F^\times \ar[r]& 1
\end{tikzcd} \]
The left group is free-by-finite by (i), and by Lemma \ref{5.2} (ii), we can use induction to reduce to the case $n=1$.

@@

\begin{proof}
Let $U = X\setminus S$ and $P_1\in U$ be a closed point. We set:
\[ C_1 = \ker(r_{P_1}|_{K^S}: K^S \to k(P_1)^\times) \]
Since $r_{P_1}|_{k^\times}:k^\times \to k(P_1)^\times$ is injective, we have $C_1\cap k^\times = 1$ and the following map is injective:
\[ C_1 \to\prod_{P\in S}\mathbb{Z},\ x \mapsto (v_P(x))_{P\in S} \]
Therefore, $C_1$ is a free abelian group of finite rank. If $C_1 = 1$, then we set $T = \{P_1\}$ and we are done. Otherwise, let $x\in C_1,\ x\neq 1$. Then there exists an $a\in k^\times$ with the following properties:
\begin{enumerate}[(i)]
\item There exists a point $P_2\in X_0\setminus(S\cup\{P_1\})$ which lies above the prime of $k(x)$ corresponding to the polynomial $x-a\in k[x]$.
\item $a$ is not a root of unity.
\end{enumerate}
We set $C_2 = \ker(r_{P_2}|_{C_1})\subset C_1$. $C_2$ is free abelian of finite rank as well. By requirement $r_{P_2}(x)=a$ and $a\in k^\times$ is not of finite order. It follows $\operatorname{rank}(C_2) < \operatorname{rank}(C_1)$. By repeating this process until $C_r=1$, we get points $P_2,\ldots,P_r\in U_0$, such that the following map is injective:
\[ C_1\to\prod_{i=2}^{r} k(P_i),\ x\mapsto(r_{P_i}(x))_i \]
Finally for $T=\{P_1,\ldots,P_r\}$, the map $r_{S,T}$ is injective. For the second assertion, note that:
\[ \operatorname{coker}(r_{S,T}) \cong\operatorname{coker}\Big(K^S/k^\times \to \prod_{P\in T}k(P)^\times /k^\times \Big) \]
Since $K^S/k^\times$ is finitely generated, Lemma \ref{5.2} (ii) and Lemma \ref{5.3} (ii) show that the latter group is free-by-finite.
\end{proof}

@@

\begin{proof}
Since any rational function on $X$ is uniquely determined by its values at those points where it is defined, $\varphi$ is unique. In other words, the following maps are injective for all finite subsets $S\subset X_0$:
\[ r_S:K^S \to\prod_{P\in X_0\setminus S} k(P)^\times,\ x\mapsto (r_P(x))_P \]
For existence, let $(S,T)$ be an admissible pair. First, we show that there is a unique homomorphism $\varphi^{S,T}$, making the following diagram commutative:
\[ (\star) \qquad \begin{tikzcd}
K'^{S'} \rar["\varphi^{S,T}", dashed] \dar["r_{S',T'}"'] & K^S \dar["r_{S,T}"]\\
\displaystyle \prod_{P\in T}k(\sigma P)^\times \rar["\prod\varphi_P"'] & \displaystyle \prod_{P\in T}k(P)^\times
\end{tikzcd} \phantom{\qquad (\star)} \]
The vertical maps are injective by definition. Thus, it suffices to show that the composition $\varrho:K'^{S'}\to\prod k(\sigma P)^\times\to \prod k(P)^\times\to\operatorname{coker}(r_{S,T})$ is trivial. Consider the commutative diagram which results from tensoring $(\star)$ with $\mathbb{Z}/n\mathbb{Z}$:
\[ \begin{tikzcd}
K'^{S'}/n \rar[dashed]\dar & K^S/n\dar\\
\displaystyle \prod_{P\in T}k(\sigma P)^\times/n \rar & \displaystyle \prod_{P\in T}k(P)^\times/n
\end{tikzcd} \]
According to Lemma~\ref{4.3} and Lemma~\ref{4.5} (ii) this diagram can now be completed by $\varphi_n: K'^{S'}/n\to K^S/n$. This implies $\varrho/n=0$, i.e. $\operatorname{im}(\varrho)\subset n\operatorname{coker}(r_{S,T})$ for every $n\in\mathbb{N}$. By Lemma~\ref{5.2} (iii) and Lemma~\ref{5.4} it follows $\varrho = 0$. By symmetry, $\varphi^S$ is an isomorphism.

Let $T_1, T_2\subset X_0\setminus S$ be two $S$-admissible subsets and suppose $T_1\subset T_2$. By observing $(\star)$ we find:
\[ r_{S,T_1}\circ\varphi^{S,T_2}=\Big(\prod_{P\in T_1}\varphi_P\Big)\circ r_{S',T_1'} = r_{S,T_1}\circ\varphi^{S,T_1} \]
Since $r_{S,T_1}$ is injective we get $\varphi^{S,T_2}=\varphi^{S,T_1}$. Hence, $\varphi^{S,T}$ is actually independent of $T$, thus we can omit the $T$ from its notation. Now if $T$ ranges over all $S$-admissible subsets of $X_0$, then $(\star)$ shows:
\[ r_S\circ\varphi^S = \Big(\prod_{P\in X_0\setminus S}\varphi_P \Big)\circ r_{S'} \]
In other words, we can replace $T$ by $X_0\setminus S$ in $(\star)$. If $S_1\subset S_2$ are two admissible subsets, then:
\[ r_{S_2}\circ\varphi^{S_2}|_{K'^{S'_1}} = \Big(\prod_{P\in X_0\setminus S_2}\varphi_P \Big)\circ r_{S'_2}|_{K'^{S'_1}} = r_{S_2}\circ\varphi^{S_1} \]
Hence, $\varphi^{S_1}=\varphi^{S_2}|_{K'^{S'_1}}$. Thus, we can combine the isomorphisms $\varphi^S$, where $S$ ranges over the admissible subsets of $X_0$, into an isomorphism $\varphi = \varinjlim \varphi^S: K'^\times \to K^\times$.

>>>>

\begin{lemma}\label{rank-dimension-inequality}
Let $v\in\operatorname{Spv}(K)$. Then we have:
\[\operatorname{rank}(v)\leq \operatorname{rrank}(v)\quad\text{and}\quad\operatorname{rrank}(v)+\dim k(v)\leq\dim(K) \]
\end{lemma}

@@

\begin{proposition}\label{2.6}
Let $K_0/K$ be an algebraic extension.
\begin{enumerate}[(i)]
\item Suppose there exists a prime number $\ell$ with $\ell^\infty\nmid[K_0:K]$ and such that for every algebraic extension $L/K_0$ we have: 
\[ \mathrm{H}^3(L,\mathbb{Z}/\ell\mathbb{Z}) = \begin{cases}
\mathbb{Z}/\ell\mathbb{Z}, & \ell^\infty\nmid [L:K_0]\\
0, & \text{otherwise}
\end{cases} \]
Then there exists a unique henselian $w\in|\operatorname{Spv}(K)|$.
\item Assume that (i) is satisfied for two different prime numbers. Then $w$ is a defectless valuation.
\end{enumerate}
\end{proposition}

@@

Now $(K_0)_{w_1}$ is henselian both with respect to $w_1$ and with respect to the prolongation of $w_0$. Lemma \ref{2.2} yields $\operatorname{cd}(G_{(K_0)_{w_1}})\leq 2$, a contradiction. The uniqueness of $w$ is again a consequence of Lemma \ref{2.2}.
\item Choose the prime $\ell$ different from $\operatorname{char} k(w)$. According to Lemma \ref{2.5} we have $\operatorname{rrank}(w)=\dim_\mathbb{Q}(\Gamma_w\otimes_\mathbb{Z}\mathbb{Q} )\geq \dim_{\mathbb{F}_\ell}(\Gamma_w /\ell\Gamma_w) = 2 = \dim(K)$. By Lemma \ref{rank-dimension-inequality}, this inequality is actually an equality.
\end{enumerate}
\end{proof}

@@

Let $v\in\operatorname{Spv}_\text{d}^{(1)}$ and let $N$ be the normal subgroup of $G_{K_v}$ generated by all subgroups $G_{K_w}$ for $w\in\operatorname{Spv}_\text{rd}^{(2)}(K)$ with $v(w) = v$. Since a global field has no non-trivial algebraic extension in which every prime splits completely, we get $N=G_{K_v}$. This shows that $K'_{v'} = (K_v)'$ is a henselization of $K'$ with respect to $v'=\sigma(v)$. Furthermore, let $w_1,w_2\in\operatorname{Spv}_\text{rd}^{(2)}(K)$ with $w_1\neq w_2$ and $v=v(w_1)=v(w_2)$, then:
\[ \sigma(G_{K^\text{t}_v}) = \sigma(G_{K_{w_1}}\cap G_{K_{w_2}}) = G_{K'_{w'_1}}\cap G_{K'_{w'_2}} = G_{(K')^\text{t}_{v'}} \]
Therefore, $\sigma$ induces an isomorphism:
\[ G_{k(v)} \cong G_{K_v}/G_{K_v^\text{t}} \to G_{K'_{v'}}/G_{(K')_{v'}^\text{t}}\cong G_{k(v')} \]
The rest follows from the Theorem of Neukirch-Uchida.
\end{proof}

@@

\begin{proof}
\begin{enumerate}[(i)]
\item  We have $(K^\text{t}_P)^\times/n\cong \mathbb{Z}/n\mathbb{Z}$ since $\operatorname{char}k(P) = 0$. The canonical map $K^\times\to (K^\text{t}_P)^\times/n$ can be identified with the map $K^\times /n\to\mathbb{Z}/n$ induced by $v_P$. Now the following commutative diagram gives us the result:
\[ \begin{tikzcd}
0 \ar[d] & 0 \ar[d]\\
U_{P'}/n \ar[r, dashed]\ar[d] & U_P/n\ar[d]\\
K'^\times /n \ar[r, "\varphi_n"]\ar[d] & K^\times/n\ar[d]\\
(K^\text{t}_P)'^\times /n \ar[r, "\varphi_n"'] &  (K^\text{t}_P)^\times /n
\end{tikzcd}\]
Note that $(K^\text{t}_P)' = (K'^{\text{t}}_{P'})$ as proven in Lemma \ref{3.2}.
\item Consider the field extension $K_P/K$. Without loss of generality, we can assume $K=K_P$. Then $r_P/n$ is an isomorphism and the composition
\[\begin{tikzcd}
k(P)^\times / n\ar[rr, "(r_P/n)^{-1}"] && U_P/n \ar[r, hook] & K_P^\times/n
\end{tikzcd}\]
is the inflation $\mathrm{H}^1(k(P), \mu_n) \to \mathrm{H}^1(K_P,\mu_n)$. The same holds for $P'$ due to Lemma \ref{3.2}. Therefore, the assertion follows from the commutativity of the following diagram:
\[ \begin{tikzcd}
k(P')^\times/n \ar[r, "\cong"] \ar[d, "\varphi_P/n"'] & \mathrm{H}^1(k(P'),\mu_n) \ar[r, "\mathrm{inf}"] \ar[d]& \mathrm{H}^1(K'_{P'}, \mu_n) \ar[d, "\varphi_n"] \\
k(P)^\times/n \ar[r, "\cong"'] & \mathrm{H}^1(k(P),\mu_n)  \ar[r, "\mathrm{inf}"'] & \mathrm{H}^1(K_{P}, \mu_n)
\end{tikzcd}  \qedhere\]
\end{enumerate}
\end{proof}

@@

\begin{example}
\begin{itemize}
\item Free or finite abelian groups are free-by-finite.
\item Finitely generated abelian groups are free-by-finite by the structure theorem for finitely generated $\mathbb{Z}$-modules.
\end{itemize}
\end{example}

\begin{lemma}\phantomsection\label{5.2}
\begin{enumerate}[(i)]
\item Let $f: A\to B$ be a homomorphism of abelian groups with finite kernel and cokernel. Then $A$ is free-by-finite iff $B$ is free-by-finite.
\item Let $0\longrightarrow A'\stackrel{i}{\longrightarrow}A\stackrel{p}{\longrightarrow}A''\longrightarrow 0$ be an exact sequence of abelian groups. If $A'$ and $A''$ are free-by-finite, then $A$ is free-by-finite. 
\item Let $0\longrightarrow A'\stackrel{i}{\longrightarrow}A\stackrel{p}{\longrightarrow}A''\longrightarrow 0$ be an exact sequence of abelian groups. If $A$ is free-by-finite, then $A'$ is free-by-finite. Additionally, if $A'$ is finitely generated, then $A''$ is free-by-finite.
\item Let $A$ be free-by-finite. Then $\bigcap_{n\in\mathbb{N}}nA=0$.
\end{enumerate}
\end{lemma}

@@

Now let $B$ be free-by-finite and $K = \ker(f)$. Since the injective map $A/K \to B$ induced by $f$ can be restricted to their torsion subgroups, we see that $(A/K)_\text{tor}$ is finite. Every $a\in A_\text{tor}$ can be written as $a = a' + k$ for some $a'\in A,\ k\in K$ such that $na'\in K$ for some $n\in\mathbb{N}$. Since both $(A/K)_\text{tor}$ and $K$ are finite, $A_\text{tor}$ is finite as well. TODO
\item TODO
\item Subgroups of free-by-finite groups are free-by-finite. Now assume $A'$ is finitely generated. We consider $A'$ as a subgroup of $A$. Let $T=A_\text{tor}$. By replacing $A'$, $A$, $A''$ with $A'/(T\cap A')$, $A/T$, $A''/p(T)$ respectively, we can assume that $A$ is free and $A'$ is free of finite rank. Let $B$ be a basis of $A$. There exists a finite subset $C\subset B$ such that $A'\subset \bigoplus_{b\in C}\mathbb{Z}b$. We get an exact sequence:
\[ 0 \longrightarrow \Big(\bigoplus_{b\in C} \mathbb{Z}b\Big)\Big/A' \longrightarrow A/A' \longrightarrow \bigoplus_{b\in B\setminus C}\mathbb{Z}b \longrightarrow 0 \]
The left abelian group is finitely generated, particularly free-by-finite. The right group is free, hence also free-by-finite. By (ii), $A/A'\cong A''$ is free-by-finite as well.
\item It suffices to show this assertion for finite groups and for $A=\mathbb{Z}$. For $A$ finite we have $nA = 0$ for $n = \#A$. Since $\mathbb{Z}$ has no nilpotent elements, the intersection of all prime ideals of $\mathbb{Z}$ is already trivial. \qedhere
\end{enumerate}
\end{proof}

@@

\begin{proof}
\begin{enumerate}[(i)]
\item Let $\mathcal{P}(F)$ be the group of principal ideals of $F$. Consider the following exact sequence:
\[ \begin{tikzcd}
1 \ar[r] & \mathcal{O}_F^\times \ar[r] & F^\times \ar[r]& \mathcal{P}(F) \ar[r] & 1
\end{tikzcd} \]
By Dirichlet's Unit Theorem, $\mathcal{O}_F^\times$ is free-by-finite. $\mathcal{P}(F)$, as a subset of the ideal group of $F$, is free abelian, in particular free-by-finite. The assertion follows from Lemma \ref{5.2} (ii).
\item Consider the following exact sequence:
\[ \begin{tikzcd}
1 \ar[r] & \displaystyle \prod_{i=1}^{n-1} F_i^\times \ar[r]& \displaystyle \Big(\prod_{i=1}^{n}F_i^\times\Big)\Big/F^\times \ar[r]& F_n^\times/F^\times \ar[r]& 1
\end{tikzcd} \]
The left group is free-by-finite by (i), and by Lemma \ref{5.2} (ii), we can use induction to reduce to the case $n=1$.

@@

\begin{proof}
Let $U = X\setminus S$ and $P_1\in U$ be a closed point. We set:
\[ C_1 = \ker(r_{P_1}|_{K^S}: K^S \to k(P_1)^\times) \]
Since $r_{P_1}|_{k^\times}:k^\times \to k(P_1)^\times$ is injective, we have $C_1\cap k^\times = 1$ and the following map is injective:
\[ C_1 \to\prod_{P\in S}\mathbb{Z},\ x \mapsto (v_P(x))_{P\in S} \]
Therefore, $C_1$ is a free abelian group of finite rank. If $C_1 = 1$, then we set $T = \{P_1\}$ and we are done. Otherwise, let $x\in C_1,\ x\neq 1$. Then there exists an $a\in k^\times$ with the following properties:
\begin{enumerate}[(i)]
\item There exists a point $P_2\in X_0\setminus(S\cup\{P_1\})$ which lies above the prime of $k(x)$ corresponding to the polynomial $x-a\in k[x]$.
\item $a$ is not a root of unity.
\end{enumerate}
We set $C_2 = \ker(r_{P_2}|_{C_1})\subset C_1$. $C_2$ is free abelian of finite rank as well. By requirement $r_{P_2}(x)=a$ and $a\in k^\times$ is not of finite order. It follows $\operatorname{rank}(C_2) < \operatorname{rank}(C_1)$. By repeating this process until $C_r=1$, we get points $P_2,\ldots,P_r\in U_0$, such that the following map is injective:
\[ C_1\to\prod_{i=2}^{r} k(P_i),\ x\mapsto(r_{P_i}(x))_i \]
Finally for $T=\{P_1,\ldots,P_r\}$, the map $r_{S,T}$ is injective. For the second assertion, note that:
\[ \operatorname{coker}(r_{S,T}) \cong\operatorname{coker}\Big(K^S/k^\times \to \prod_{P\in T}k(P)^\times /k^\times \Big) \]
Since $K^S/k^\times$ is finitely generated, Lemma \ref{5.2} (iii) and Lemma \ref{5.3} (ii) show that the latter group is free-by-finite.
\end{proof}

@@

\begin{proof}
Since any rational function on $X$ is uniquely determined by its values at those points where it is defined, $\varphi$ is unique. In other words, the following maps are injective for all finite subsets $S\subset X_0$:
\[ r_S:K^S \to\prod_{P\in X_0\setminus S} k(P)^\times,\ x\mapsto (r_P(x))_P \]
For existence, let $(S,T)$ be an admissible pair. First, we show that there is a unique homomorphism $\varphi^{S,T}$, making the following diagram commutative:
\[ (\star) \qquad \begin{tikzcd}
K'^{S'} \rar["\varphi^{S,T}", dashed] \dar["r_{S',T'}"'] & K^S \dar["r_{S,T}"]\\
\displaystyle \prod_{P\in T}k(\sigma P)^\times \rar["\prod\varphi_P"'] & \displaystyle \prod_{P\in T}k(P)^\times
\end{tikzcd} \phantom{\qquad (\star)} \]
The vertical maps are injective by definition. Thus, it suffices to show that the composition $\varrho:K'^{S'}\to\prod k(\sigma P)^\times\to \prod k(P)^\times\to\operatorname{coker}(r_{S,T})$ is trivial. Consider the commutative diagram which results from tensoring $(\star)$ with $\mathbb{Z}/n\mathbb{Z}$:
\[ \begin{tikzcd}
K'^{S'}/n \rar[dashed]\dar & K^S/n\dar\\
\displaystyle \prod_{P\in T}k(\sigma P)^\times/n \rar & \displaystyle \prod_{P\in T}k(P)^\times/n
\end{tikzcd} \]
According to Lemma~\ref{4.3} and Lemma~\ref{4.5} (ii) this diagram can now be completed by $\varphi_n: K'^{S'}/n\to K^S/n$. This implies $\varrho/n=0$, i.e. $\operatorname{im}(\varrho)\subset n\operatorname{coker}(r_{S,T})$ for every $n\in\mathbb{N}$. By Lemma~\ref{5.2} (iii) and Lemma~\ref{5.4} it follows $\varrho = 0$. By symmetry, $\varphi^{S,T}$ is an isomorphism.

Let $T_1, T_2\subset X_0\setminus S$ be two $S$-admissible subsets and suppose $T_1\subset T_2$. By considering $(\star)$ we find:
\[ r_{S,T_1}\circ\varphi^{S,T_2}=\Big(\prod_{P\in T_1}\varphi_P\Big)\circ r_{S',T_1'} = r_{S,T_1}\circ\varphi^{S,T_1} \]
Since $r_{S,T_1}$ is injective we get $\varphi^{S,T_2}=\varphi^{S,T_1}$. Hence, $\varphi^{S,T}$ is actually independent of $T$, thus we can omit the $T$ from its notation. Now if $T$ ranges over all $S$-admissible subsets of $X_0$, then $(\star)$ shows:
\[ r_S\circ\varphi^S = \Big(\prod_{P\in X_0\setminus S}\varphi_P \Big)\circ r_{S'} \]
In other words, we can replace $T$ by $X_0\setminus S$ in $(\star)$. If $S_1\subset S_2$ are two admissible subsets, then:
\[ r_{S_2}\circ\varphi^{S_2}|_{K'^{S'_1}} = \Big(\prod_{P\in X_0\setminus S_2}\varphi_P \Big)\circ r_{S'_2}|_{K'^{S'_1}} = r_{S_2}\circ\varphi^{S_1} \]
Hence, $\varphi^{S_1}=\varphi^{S_2}|_{K'^{S'_1}}$. Thus, we can combine the isomorphisms $\varphi^S$, where $S$ ranges over the admissible subsets of $X_0$, into an isomorphism $\varphi = \varinjlim \varphi^S: K'^\times \to K^\times$.
